Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-17 paper-webserver.tex
ADD: new first para for implementation

\section{IMPLEMENTATION}
% para
% goals: predictive analylitcs in minutes, storage up 50,000-100,000 genomes {}

% Inputs: more like going from file -> analysis -> graph db (not a hard subsection)
Spfy takes assembled genomes as input, runs selected analyses modules, and converts the results into a graph structure for upload.

% Outputs: more like what we query from blazegraph and how we use it (not a hard subsection)
Spfy queries the graph database to run analyses XYZ and build visualizations.

>>>>

\section{IMPLEMENTATION}
% para: the semantic web
Spfy is built around semantic web technologies which focuses on describing the relaions between different datum \cite{berners2001semantic}.
In biological data, a semantic web focus describes individual data points by the type, for example as a genome, contiguous DNA sequence, or gene, and then link related data together in a queryable graph.
Semantic web technlogies allow new, not previously described data to be seemlessly incorporated to the existing graph, and has been proposed as a common standard for the open sharing of data \cite{horrocks2005semantic}.
